A note on multi agent learning

### 2016-06-27 multiAgentLearning/paper/article.tex
spelling and todos

\section{Core algorithm}
The core algorithm as presented by \citep{herbert} and formalized by
\citep{karandikar} \todo[inline]{karandikars algorithm is different..}
can be seen bellow:

\begin{enumerate}
  \item $ \begin{cases}
              \text{if } \pi_t \geq \alpha_t & A_{t+1} = A_t\\
              \text{else} & A_{t+1} \neq A_t
              \end{cases}$
  \item $ \alpha_{t+1} = \lambda \alpha_t + (1-\lambda) \pi_t $ \\
\end{enumerate}
\begin{tabular}{ll}
  Definition & symbol \\ \toprule
  Time & $t$ \\
  Action & $A_t$ \\
  Utility & $\pi_t$ \\
  Aspiration & $\alpha_t$ \\
  Learning rate & $\lambda$ \\ \bottomrule
\end{tabular}

@@

\section{Iterated prisoners dilemma}
\drafting
To demonstrate a potential use of this algorithm we will use at several example
cases. The first one being the iterated prisoners dilemma. Consider
the following normal form game:

\begin{tabular}{lll}
            & Cooperate   & Defect \\
  Cooperate & $(2,2)$     & $(0,3)$  \\
  Defect    & $(3,0)$     & $(1,1)$  \\
\end{tabular}

The Nash equilibrium of this game lies on Defect,Defect. However, all but
that action are pareto optimal actions. So the Nash equilibrium would be the
``right'' strategy to play if the game is only played once, but if you repeat
the game against the same opponent, interestingly enough you can ``solve''
the prisoners dilemma by ``teaching'' the opponent to cooperate.

However strategies such as tit for tat or win stay lose shift already know
which actions are winning and which are punishing to try and solve it.
Satisficing play learns this however by updating the aspiration it got from
playing a move. If we consider a game vs always cooperate for example:

@@

And finally vs tit for tat, a game which can also be found in the
\citep{stimpson:2001} paper:

\todo{copy table}
\section{Properties of satisifing play}
\drafting

Using both \citep{karandikar} and \citep{stimpson:2001} works to look deeper
at the properties of satisifing play.

karandikar used a theoretical proofing method, wehreas stimpson showed some
experimental results.

@@

\begin{tabular}{ll}
  Definition & symbol \\ \toprule
  Time & $t$ \\
  Action & $A_t$ \\
  Utility & $\pi_t$ \\
  Aspiration & $\alpha_t$ \\
  Learning rate & $\lambda$ \\ \bottomrule
\end{tabular}

@@

\todo{check }
\bibliography{main}

>>>>

\section{Core algorithm}
The core algorithm as presented by \citep{herbert} and formalized by
\citep{karandikar},
in here we present the simplified version of \citep{stimpson:2001} first:

\begin{enumerate}
  \item $ \begin{cases}
              \text{if } \pi_t \geq \alpha_t & A_{t+1} = A_t\\
              \text{else} & A_{t+1} \neq A_t
              \end{cases}$
  \item $ \alpha_{t+1} = \lambda \alpha_t + (1-\lambda) \pi_t $ \\
\end{enumerate}
\todo{add table caption}
\begin{tabular}{ll}
  Definition & symbol \\ \toprule
  Time & $t$ \\
  Action & $A_t$ \\
  Utility & $\pi_t$ \\
  Aspiration & $\alpha_t$ \\
  Learning rate & $\lambda$ \\ \bottomrule
\end{tabular}

@@

\section{Iterated prisoner's dilemma}
\drafting
To demonstrate a potential use of this algorithm we will use at several example
cases. The first one being the iterated prisoner's dilemma. Consider
the following normal form game:

\todo{add table caption}
\begin{tabular}{lll}
            & Cooperate   & Defect \\
  Cooperate & $(2,2)$     & $(0,3)$  \\
  Defect    & $(3,0)$     & $(1,1)$  \\
\end{tabular}

The Nash equilibrium of this game lies on Defect,Defect. However, all but
that action are pareto optimal actions. So the Nash equilibrium would be the
``right'' strategy to play if the game is only played once, but if you repeat
the game against the same opponent, interestingly enough you can ``solve''
the prisoner's dilemma by ``teaching'' the opponent to cooperate.
\todo{can one really solve? Is it really teaching? should either add references
or change wording}

However strategies such as tit for tat or win stay lose shift already know
which actions are winning and which are punishing to try and solve it.
Satisficing play learns this however by updating the aspiration it got from
playing a move. If we consider a game versus always cooperate for example:

@@

And finally versus tit for tat, a game which can also be found in the
\citep{stimpson:2001} paper:

\todo{copy table}
\section{Properties of satisficing play}
\drafting

Using both \citep{karandikar} and \citep{stimpson:2001} works to look deeper
at the properties of satisficing play.

karandikar used a theoretical proofing method, whereas Stimpson showed some
experimental results.

@@

@@

\todo{add caption for tables?}
\bibliography{main}
